Pillar 2 - Topic Modeling

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
function to view LDA

```{r plot_tf_idf}
plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){

@@

# LDA
## Fitting Model
```{r}
my_cast_tdm <- function(data, level) data %>%
  count(Code, word) %>%
  cast_dtm(Code, word, n)

d_description_cast <- my_cast_tdm(d_description)
d_overview_cast <- my_cast_tdm(d_overview)
d_manual_cast <- my_cast_tdm(d_manual)
```

@@

  # Setup
  topic_letter <- tibble(topic_number = 1:26,
                         topic_letter = c(topic_names,
                                          paste("Topic", LETTERS[(length(topic_names)+1) : 26])))

  # Beta Distribution: term-topic
  term_topic <- tidy(results, matrix = "beta") %>%
    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
    mutate(topic = topic_letter) %>%
    select(-topic_letter)

  term_topic %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup %>%
    ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Gamma Distribution: document-topic
  doc_topic <- tidy(results, matrix = "gamma") %>%
    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
    mutate(topic = topic_letter,
           facet = document) %>%
    select(-c(topic_letter, document))

  if(facet) doc_topic <- separate(doc_topic, facet, c("document", "facet"), sep = "_") %>%
    add_count(facet) %>%
    group_by(facet, topic) %>%
    summarise(gamma = sum(gamma)) %>%
    ungroup

  # Plot 1
  doc_topic %>%
    filter(gamma > 0.05) %>%
    ggplot(aes(reorder_within(facet, by = gamma, within = topic), y = gamma, fill = facet)) +
    geom_col(show.legend = F) +
    facet_rep_wrap(~ topic, scales = "free",
                   repeat.tick.labels = "bottom") +
    scale_x_reordered() +
    coord_flip() +
    labs(x = "(Group of) Courses", y = "Gamma", title = "Main Courses/Clusters of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

>>>>

```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, plot_id = NULL){

@@

# LDA
## Fitting Model
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(Code, word) %>%
  cast_dtm(Code, word, n)

d_description_cast <- my_cast_tdm(d_description)
d_overview_cast <- my_cast_tdm(d_overview)
d_manual_cast <- my_cast_tdm(d_manual)

rm(my_cast_tdm)
```

@@

  # Beta distribution
  tidy(LDA_description_10, matrix = "beta") %>%
    mutate(topic = paste("Topic", topic)) %>%
    group_by(topic) %>%
      top_n(10, beta) %>%
    ungroup %>%

  ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Gamma Distribution
  data_gamma <- tidy(LDA_description_10, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(Code = document) %>%
    left_join(select(d_course, Code, Cluster, Concentration, `Concentration (additional)`), by = "Code")

  if(ensym(facet) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = Code)

  if(ensym(facet) == sym("Cluster")) data_gamma <- data_gamma %>%
                                       filter(is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(facet) == sym("Concentration")) data_gamma <- data_gamma %>% 
                                             filter(!is.na(Concentration)) %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

  # Gamma Distribution: plot 1 docu-topic
  data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = sum(gamma))
    filter(gamma > 0.05) %>%
    ggplot(aes(reorder_within(facet, by = gamma, within = topic), y = gamma, fill = facet)) +
    geom_col(show.legend = F) +
    facet_rep_wrap(~ topic, scales = "free",
                   repeat.tick.labels = "bottom") +
    scale_x_reordered() +
    coord_flip() +
    labs(x = "(Group of) Courses", y = "Gamma", title = "Main Courses/Clusters of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))
